Apache Storm

### 2017-12-15 paper.tex
Checkpoint before revert to three main chapters
Added bibliography and made minor section changes

\institute{\email{st152995@stud.uni-stuttgart.de}}

@@

\textbf{Data} today is generated by a lot of devices that are connected to the internet and the amount of data being generated at any instance is increasing rapidly. These devices could include a personal computer, a smart phone, or even an embedded device. Due to the rapid adoption of Internet of Things, data is being generated at an unprecedented rate. The sheer volume of data generated and the rate at which it is being generated can be termed as Big Data. \textbf{Big Data} made it's appearance in 1998 SGI slide by John Mashey and now is of interest to a lot of financial as well as research institutions.[1]

Data can be considered the oil of this present age, because with huge amounts of data one can determine hidden patterns. A lot of companies utilize pattern recognition on big data to open opportunities for revenue generation whereas research institutions use it to discover patterns simply not observable by the human mind(simply due to the volume of data). The question on how to classify any data as big data can be answered by using the 3Vs: Volume, Variety and Velocity [2]. Any data with big volume or variety (such as text, video, images, etc) or that gets generated rapidly can be considered as big data. In this paper regarding \textbf{Apache Storm} we consider the third V of big data to be the influencing factor.

@@

Apache storm is one of the available open source tools for stream data processing, which is considered to be one of the most easy to use, fast and fault tolerant systems available [3]. These three factors have been the major points for the general public to choose \textbf{Apache Storm} above other available tools. It was originally created by Nathan Marz at BackType and till now, at present more than 60 companies use or experiment with this tool.

\subsection{Architecture}
The basic Storm data processing architecture consists of stream of tuples flowing through a defined topology to yield the required analytic result. Processing of this stream data is performed in Nodes called the worker nodes, which are responsible for performing the required calculations. There is also another node named the Master Node, which is responsible for the complete Storm infrastructure,  by keeping track of all the worker nodes and the total topology itself.

@@

\paragraph{The Master node} also called the \textbf{Nimbus} is also responsible for distribution and coordination of the execution of topologies. The Nimbus is the first point where the user submits the defined topology, which is then distributed among the worker nodes.  Figure \ref{fig:arch} illustrates the high level architecture where, Nimbus monitors all the available worker nodes and both the nimbus as well as the worker nodes use \textbf{Apache Zookeeper} to store their states. The actual processing is done by the \textbf{worker nodes}, and each worker node runs multiple Worker Processes each of them mapped to their own topology [4]. It is also worth while noting that multiple worker processes in a worker node could be executing different parts of the topology.

\subsubsection{Worker Node}
\paragraph{Worker Node} is responsible for all the heavy lifting required for processing of the topology. One worker node may run a multiple number of worker processes. Each of these worker processes may belong to the same topology or different topologies. A worker node maintains a \textbf{Supervisor} and a multiple number of Worker Processes which in turn maintains a multiple number of executors. Thus, Executors enable intra-topology parallelism whereas Tasks provide intra-spout or intra-bolt parallelism. Figure \ref{fig:workerarch} depicts the design of a Worker node.[4]

@@

\paragraph{Executors} are made up of one or multiple Tasks. Unless specified explicitly, storm assigns single task to a single executor. Executors takes tuples from the in queue, examines the task this tuple is destined to, performs the task and then places the result in the out queue [4].

@@

\section{System Design}
Storm server clusters as discussed above in Section \ref{sec:concepts}, requires at least a Master node and a series of Worker nodes. Apart from these, it also requires zookeeper to keep track of the status of all the master as well as the worker nodes. Setup of these nodes are trivial and can be configured easily in storm using the configuration files. But, the design of a system with regard to the requirements is not such a trivial task because of the different data processing needs. The things to consider while designing a Storm Solution is the System architecture i.e. Lambda or Lambda-less. After selecting one of the above solution, further decisions for the topology design should be considered.

\subsection{System Architecture}
Apache storm is a flexible software which is capable of adapting to the requirements. It can be used in a lambda architecture or a lambda less architecture.Depending upon the requirements of the system, one can opt for either of the above solutions

\subsubsection{Lambda-less Architecture}
\paragraph{Apache Storm} can handle data processing without the need of persistence layer and offers its own 
resiliency mechanisms to make sure data is tuples injected into the system are processed. It has two types of processing schemes, \textbf{at least once} where each tuple is processed as the name suggests, at least once, and the other \textbf{at most once}, where the tuples are either processed once or dropped in cases of failure. To provide \textbf{at least once} semantics, Storm maintains an acker bolt, which keeps track of the tuple flow in the directed acyclic graph.

\begin{figure}
  \begin{center}
    \includegraphics[width=.7\textwidth]{acker.png}
    \caption{Storm Acker Bolt [4]}
    \label{fig:acker}
   \end{center}
\end{figure}

Figure \ref{fig:acker} shows the Acker bolt integration with the storm topology. It keeps track of the tuple flow starting from the point where it has been injected into the topology till it leaves the topology. After the tuple has left the topology, an \textbf{ack} is sent to the Spout, at this point, it can decide to remove the Tuple from memory.

@@

Data is persisted in the persistence layer so that in cases of high data volume, Batch processing can be done on the input data to provide guaranteed processing and to reduce the computation requirement on the Real Time Data Processing Unit.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{ranking.png}
    \caption{Example Ranking Topologies}
    \label{fig:ranking}
   \end{center}
\end{figure}

\section{Practical Use Case}
Apache Storm is used for stream processing of data, in many sources [2,3] a word frequency count example has been shown which can be considered to be trivial, but in actual practice it can be used to execute complicated algorithms. For the purposes of this paper we consider a trivial but different example of \textbf{Sentiment Analysis}.

@@

\end{document}

>>>>

\institute{\email{aanal.basaula@gmail.com}}

@@

\textbf{Data} today is generated by a lot of devices that are connected to the internet and the amount of data being generated at any instance is increasing rapidly. These devices could include a personal computer, a smart phone, or even an embedded device. Due to the rapid adoption of Internet of Things, data is being generated at an unprecedented rate. The sheer volume of data generated and the rate at which it is being generated can be termed as Big Data. \textbf{Big Data} made it's appearance in 1998 SGI slide by John Mashey and now is of interest to a lot of financial as well as research institutions.\cite{miningstatus}

Data can be considered the oil of this present age, because with huge amounts of data one can determine hidden patterns. A lot of companies utilize pattern recognition on big data to open opportunities for revenue generation whereas research institutions use it to discover patterns simply not observable by the human mind(simply due to the volume of data). The question on how to classify any data as big data can be answered by using the 3Vs: Volume, Variety and Velocity \cite{usingapachestorm}. Any data with big volume or variety (such as text, video, images, etc) or that gets generated rapidly can be considered as big data. In this paper regarding \textbf{Apache Storm} we consider the third V of big data to be the influencing factor.

@@

Apache storm is one of the available open source tools for stream data processing, which is considered to be one of the most easy to use, fast and fault tolerant systems available \cite{stormperspective}. These three factors have been the major points for the general public to choose \textbf{Apache Storm} above other available tools. It was originally created by Nathan Marz at BackType and till now, at present more than 60 companies use or experiment with this tool.

\subsection{Architecture Overview}
The basic Storm data processing architecture consists of stream of tuples flowing through a defined topology to yield the required analytic result. Processing of this stream data is performed in Nodes called the worker nodes, which are responsible for performing the required calculations. There is also another node named the Master Node, which is responsible for the complete Storm infrastructure,  by keeping track of all the worker nodes and the total topology itself.

@@

\paragraph{The Master node} also called the \textbf{Nimbus} is also responsible for distribution and coordination of the execution of topologies. The Nimbus is the first point where the user submits the defined topology, which is then distributed among the worker nodes.  Figure \ref{fig:arch} illustrates the high level architecture where, Nimbus monitors all the available worker nodes and both the nimbus as well as the worker nodes use \textbf{Apache Zookeeper} to store their states. The actual processing is done by the \textbf{worker nodes}, and each worker node runs multiple Worker Processes each of them mapped to their own topology \cite{stormtwitter}. It is also worth while noting that multiple worker processes in a worker node could be executing different parts of the topology.

\subsubsection{Worker Node}
\paragraph{Worker Node} is responsible for all the heavy lifting required for processing of the topology. One worker node may run a multiple number of worker processes. Each of these worker processes may belong to the same topology or different topologies. A worker node maintains a \textbf{Supervisor} and a multiple number of Worker Processes which in turn maintains a multiple number of executors. Thus, Executors enable intra-topology parallelism whereas Tasks provide intra-spout or intra-bolt parallelism. Figure \ref{fig:workerarch} depicts the design of a Worker node.\cite{stormtwitter}

@@

\paragraph{Executors} are made up of one or multiple Tasks. Unless specified explicitly, storm assigns single task to a single executor. Executors takes tuples from the in queue, examines the task this tuple is destined to, performs the task and then places the result in the out queue \cite{stormtwitter}.

@@

\section{Stream Processing}
A stream is a continuous flow of data from one point to the another. A Stream Processing system works on these data streams, the work may just be simple transformations, but also could be as complex as predictive analysis. A stream processing system depending on the nature of application has different requirements.

Let us consider a Streaming service (may it be video or audio), which performs some transformations on the data stream before serving the client. A loss in packets is not a major problem as a little degradation in Quality for a short period of time is acceptable in this scenario. As a counter example scenario, consider a service that keeps track of the stream of purchases, it is necessary to not miss any of these important data. Apart from this, we also need to consider various other factors for design of a stream processing system, such as resilience, scalability, etc. These considerations will be scrutinized in this section.

\subsection{System Architecture}
As discussed above, a system depending upon the requirement is allowed to drop a few data sets thus allowing us to utilize the lambda-less architecture, whereas others require complete data sets therefore utilizing the Lambda Architecture.

\subsubsection{Lambda-less Architecture}
\paragraph{Apache Storm} can handle data processing without the need of persistence layer and offers its own 
resiliency mechanisms to make sure data is tuples injected into the system are processed. Section \ref{sec:resilience} explains in further detail how storm tries and guarantees a reliable throughput.

Lambda less architectures are not reliable and do not tend to provide persistence storage as every result is stored in memory and is suitable only for systems which require no storage of calculated information. In section \ref{sec:usecase}

@@

Data is persisted in the persistence layer so that in cases of high data volume, Batch processing can be done on the input data to provide guaranteed processing and to reduce the computation requirement on the Real Time Data Processing Unit.\cite{lambdastorm}

@@

\subsection{Storm Resilience}
\label{sec:resilience}

It has two types of processing schemes, \textbf{at least once} where each tuple is processed as the name suggests, at least once, and the other \textbf{at most once}, where the tuples are either processed once or dropped in cases of failure. To provide \textbf{at least once} semantics, Storm maintains an acker bolt, which keeps track of the tuple flow in the directed acyclic graph.

\begin{figure}
  \begin{center}
    \includegraphics[width=.7\textwidth]{acker.png}
    \caption{Storm Acker Bolt \cite{stormtwitter}}
    \label{fig:acker}
   \end{center}
\end{figure}

\paragraph{Figure} \ref{fig:acker} shows the Acker bolt integration with the storm topology. It keeps track of the tuple flow starting from the point where it has been injected into the topology till it leaves the topology. After the tuple has left the topology, an \textbf{ack} is sent to the Spout, at this point, it can decide to remove the Tuple from memory.

\section{Practical Use Case}
\label{sec:usecase}
Apache Storm is used for stream processing of data, in many sources [2,3] a word frequency count example has been shown which can be considered to be trivial, but in actual practice it can be used to execute complicated algorithms. For the purposes of this paper we consider a trivial but different example of \textbf{Sentiment Analysis}.

@@

 The zookeeper services can be run in a single machine or can be deployed in a cluster as well. A single zookeeper instance can also be shared between other services and Apache Storm, but, the major consideration to be taken into account is performance. If there are multiple number of systems that utilize the zookeeper, the Zookeeper can run out of number of clients it can service, thus affecting up-time of the systems in general.\cite{stormtwitter} Whereas having a dedicated Zookeeper allows a high performing cluster.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Bibliography}
\bibliographystyle{splncs03}
\bibliography{paper}
Alle Links wurden zuletzt am 22.06.2015 geprüft.
\end{document}
